---
title: "compare estimation with model-fitting"
output: html_notebook
author: ruonanjia
---


```{r}
library(tidyverse)
library(ggplot2)
```

Functions
```{r}
# functions
data_summary <- function(data, varname, groupnames){
  # Function to calculate the mean and the standard error
  # for each group
  #+++++++++++++++++++++++++
  # data : a data frame
  # varname : the name of a column containing the variable
  #to be summariezed
  # groupnames : vector of column names to be used as
  # grouping variables
  
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

data_meanstd <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)
  ymax <- m+sd(x)
  return(c(y=m,ymin=ymin,ymax=ymax))
}

data_meanse <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)/sqrt(length(x))
  ymax <- m+sd(x)/sqrt(length(x))
  return(c(y=m,ymin=ymin,ymax=ymax))
}
```

Load data
```{r}
path <- "E:/Ruonan/Projects in the lab/MDM Project/Medical Decision Making Imaging/MDM_imaging/Behavioral Analysis/Behavior Analysis"
setwd(path)
load("data_all_01272020.rda")

data_all$beta_t <- -data_all$beta

fit <- read.csv('MDM_model_fitting_parameters.csv', header = TRUE)
```

Take out the model-fitted parameters, monetary decisions
```{r}
fit_mon <- fit[fit$model== 'ambigNrisk' & fit$fitby == 'value', ] 
```

Calculate the model-fitting probability for ambiguity levels
```{r}
ambigs <- c(0.24, 0.5, 0.74)

fit_mon$fit_prob_a24 <- 0.5 - ambigs[1]/2*fit_mon$beta
fit_mon$fit_prob_a50 <- 0.5 - ambigs[2]/2*fit_mon$beta
fit_mon$fit_prob_a74 <- 0.5 - ambigs[3]/2*fit_mon$beta

fit_prob <- data.frame(id = fit_mon$id, is_med = fit_mon$is_med,
                       fit_prob_a24 = fit_mon$fit_prob_a24 *100, 
                       fit_prob_a50 = fit_mon$fit_prob_a50*100, 
                       fit_prob_a74 = fit_mon$fit_prob_a74*100)
```

combine table
```{r}
data <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med == 0, ]

data <- merge(data, fit_prob, by=intersect(colnames(data), colnames(fit_prob)))
# data <- data_all
```

reorganize sheet
```{r}

idx = 1
for (amb_level in c("24", "50", "74")) {
  
  for (out_level in c("1", "2", "3", "4")) {
    estimate_single = data %>% select((id:is_med), contains(paste("estimate_", amb_level, "_", out_level, sep = "")), contains(paste("fit_prob_a", amb_level, sep = "")))
    estimate_single$out_level = as.numeric(out_level)
    estimate_single$amb_level = as.numeric(amb_level)
    names(estimate_single)[3] = "estimate_amb" 
    names(estimate_single)[4] = "fit_prob_amb"
    
    # estimate_mon = data[data$is_med == 0,] %>% select((id), eval(parse(paste("estimate_", amb_level, "_", out_level, sep = ""))))
    # estimate_mon$out_level = as.numeric(out_level)
    # estimate_mon$amb_level = as.numeric(amb_level)
    
    if (idx == 1) {
      estimate = estimate_single
    } else {
      estimate = rbind(estimate, estimate_single)
    }
    
    idx = idx + 1
  }
  
}

estimate$out_level = as.factor(estimate$out_level)
estimate$amb_level = as.factor(estimate$amb_level)
```

Calculate average
```{r}
id <- unique(estimate$id)
length(id)

   
```

Plot estimation by ambiguity level and outcome level
```{r}
# if want to exclude participants
names(estimate)

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med, ]

tb2plot = data_summary(estimate_plot, varname = "estimate_amb", groupnames = c("amb_level", "out_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = estimate_amb, fill = out_level)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate_amb-sd, ymax=estimate_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Estimation of outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```

Plot model-fitted probability by ambiguity level 
```{r}
# if want to exclude participants
names(estimate)

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

tb2plot = data_summary(estimate_plot, varname = "fit_prob_amb", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = fit_prob_amb)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=fit_prob_amb-sd, ymax=fit_prob_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Model-fitted outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```


```{r}
is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

estimate_plot$estimate_amb_mean <- rowMeans(data.frame(
  out1 = estimate$estimate_amb[estimate$out_level == 1],
  out2 = estimate$estimate_amb[estimate$out_level == 2],
  out3 = estimate$estimate_amb[estimate$out_level == 3],
  out4 = estimate$estimate_amb[estimate$out_level == 4]
))

tb2plot = data_summary(estimate_plot, varname = "estimate_amb_mean", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = estimate_amb_mean)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate_amb_mean-sd, ymax=estimate_amb_mean+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Estimated mean outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))
```

Compare estimated and model-fitted outcome probability
```{r}

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

estimate_plot$estimate_amb_mean <- rowMeans(data.frame(
  out1 = estimate$estimate_amb[estimate$out_level == 1],
  out2 = estimate$estimate_amb[estimate$out_level == 2],
  out3 = estimate$estimate_amb[estimate$out_level == 3],
  out4 = estimate$estimate_amb[estimate$out_level == 4]
))

compare <- rbind(
  data.frame(
    id = estimate_plot$id,
    amb_level = estimate_plot$amb_level,
    prob = estimate_plot$estimate_amb_mean,
    method = rep("estimate", nrow(estimate_plot))
  ), 
  data.frame(
    id = estimate_plot$id,
    amb_level = estimate_plot$amb_level,
    prob = estimate_plot$fit_prob_amb,
    method = rep("model-fit", nrow(estimate_plot))
  )
)

tb2plot = data_summary(compare, varname = "prob", groupnames = c("amb_level","method"))

ggplot(data = tb2plot, aes(x = amb_level, y = prob, fill = method)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=prob-sd, ymax=prob+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Compare estimated and model-fitted outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
