---
title: "R Notebook"
output: html_notebook
---

```{r}
rm(list=ls())
```


```{r}
library(ggplot2)
```

Read data
```{r}
path <- "E:/Ruonan/Projects in the lab/MDM Project/Medical Decision Making Imaging/MDM_imaging/Behavioral Analysis/Behavior Analysis"
setwd(path)

load("data_all_01272020.rda") # value constrained between 0-50
data_50 <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med==0, ]
# data <- data_all]
data_50$beta_t <- -data_50$beta

load("data_all_05142020.rda") # value constrained between 0-100
data_100 <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med==0, ]
# data <- data_all
data_100$beta_t <- -data_100$beta

load("data_all_05222020.rda") # value constrained between 0-100, grid search
data_100_grid <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med==0, ]
# data <- data_all
data_100_grid$beta_t <- -data_100_grid$beta

```


check value fitted by differet constraints
```{r}
for (sub_idx in 1:sum(data_50$is_med==0)) {
  sub_id <- data_50$id[sub_idx]
  # val_50 <- c(data_50$val1[sub_idx], data_50$val2[sub_idx], data_50$val3[sub_idx], data_50$val4[sub_idx])
  # val_100 <- c(data_100_grid$val1[sub_idx], data_100_grid$val2[sub_idx], data_100_grid$val3[sub_idx], data_100_grid$val4[sub_idx])
  # 
  # plot(val_50, val_100, main = sub_id)
  
  val_100 <- c(data_100$val1[sub_idx], data_100$val2[sub_idx], data_100$val3[sub_idx], data_100$val4[sub_idx])
  val_100_grid <- c(data_100_grid$val1[sub_idx], data_100_grid$val2[sub_idx], data_100_grid$val3[sub_idx], data_100_grid$val4[sub_idx])
  
  plot(val_100, val_100_grid, main = sub_id)  
  
  # val <- data.frame(val_50, val_100)
  # 
  # f <- ggplot(val, aes(x=val_50, y=val_100)) +
  #   geom_point() +
  #   scale_x_continuous(limits = c(0,50)) +
  #   scale_y_continuous(limits = c(0, 100)) +
  #   ggtitle(sub_id)
  # 
  # print(f)
}
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
