---
title: "compare estimation with model-fitting"
output: html_notebook
author: ruonanjia
---

# Packages and functions
```{r}
library(tidyverse)
library(ggplot2)
library(viridis)
library(minpack.lm)


```

Functions
```{r}
# functions
data_summary <- function(data, varname, groupnames){
  # Function to calculate the mean and the standard error
  # for each group
  #+++++++++++++++++++++++++
  # data : a data frame
  # varname : the name of a column containing the variable
  #to be summariezed
  # groupnames : vector of column names to be used as
  # grouping variables
  
  require(plyr)
  summary_func <- function(x, col){
    c(mean = mean(x[[col]], na.rm=TRUE),
      sd = sd(x[[col]], na.rm=TRUE)/sqrt(length(x[[col]])))
  }
  data_sum<-ddply(data, groupnames, .fun=summary_func,
                  varname)
  data_sum <- rename(data_sum, c("mean" = varname))
  return(data_sum)
}

data_meanstd <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)
  ymax <- m+sd(x)
  return(c(y=m,ymin=ymin,ymax=ymax))
}

data_meanse <- function(x) {
  # Function to produce summary statistics (mean and +/- sd)
  m <- mean(x)
  ymin <- m-sd(x)/sqrt(length(x))
  ymax <- m+sd(x)/sqrt(length(x))
  return(c(y=m,ymin=ymin,ymax=ymax))
}
```

#Compare model-estimated probability and subjective estimation of probability
## Load data
```{r}
path <- "E:/Ruonan/Projects in the lab/MDM Project/Medical Decision Making Imaging/MDM_imaging/Behavioral Analysis/Behavior Analysis"
setwd(path)
load("data_all_01272020.rda")

data_all$beta_t <- -data_all$beta

fit <- read.csv('MDM_model_fitting_parameters.csv', header = TRUE)
```

Take out the model-fitted parameters, monetary decisions
```{r}
fit_mon <- fit[fit$model== 'ambigNrisk' & fit$fitby == 'value', ] 
```

Calculate the model-fitting probability for ambiguity levels
```{r}
ambigs <- c(0.24, 0.5, 0.74)

fit_mon$fit_prob_a24 <- 0.5 - ambigs[1]/2*fit_mon$beta
fit_mon$fit_prob_a50 <- 0.5 - ambigs[2]/2*fit_mon$beta
fit_mon$fit_prob_a74 <- 0.5 - ambigs[3]/2*fit_mon$beta

fit_mon$fit_prob_a24 = fit_mon$fit_prob_a24 *100 
fit_mon$fit_prob_a50 = fit_mon$fit_prob_a50*100 
fit_mon$fit_prob_a74 = fit_mon$fit_prob_a74*100

# fit_prob <- data.frame(id = fit_mon$id,
#                        is_med = fit_mon$is_med,
#                        )

fit_mon
```

combine table
```{r}
data <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med == 0, ]

data <- merge(data, fit_mon, by=intersect(colnames(data), colnames(fit_mon)))
data
```

reorganize sheet
```{r}

idx = 1
for (amb_level in c("24", "50", "74")) {
  
  for (out_level in c("1", "2", "3", "4")) {
    estimate_single = data %>% select((id:is_med), contains(paste("estimate_", amb_level, "_", out_level, sep = "")), contains(paste("fit_prob_a", amb_level, sep = "")))
    estimate_single$out_level = as.numeric(out_level)
    estimate_single$amb_level = as.numeric(amb_level)
    names(estimate_single)[3] = "estimate_amb" 
    names(estimate_single)[4] = "fit_prob_amb"
    
    # estimate_mon = data[data$is_med == 0,] %>% select((id), eval(parse(paste("estimate_", amb_level, "_", out_level, sep = ""))))
    # estimate_mon$out_level = as.numeric(out_level)
    # estimate_mon$amb_level = as.numeric(amb_level)
    
    if (idx == 1) {
      estimate = estimate_single
    } else {
      estimate = rbind(estimate, estimate_single)
    }
    
    idx = idx + 1
  }
  
}

estimate$out_level = as.factor(estimate$out_level)
estimate$amb_level = as.factor(estimate$amb_level)
```

Calculate average
```{r}
id <- unique(estimate$id)
length(id)

   
```

Plot estimation by ambiguity level and outcome level
```{r}
# if want to exclude participants
names(estimate)

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med, ]

tb2plot = data_summary(estimate_plot, varname = "estimate_amb", groupnames = c("amb_level", "out_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = estimate_amb, fill = out_level)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate_amb-sd, ymax=estimate_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Estimation of outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```

Plot model-fitted probability by ambiguity level 
```{r}
# if want to exclude participants
names(estimate)

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

tb2plot = data_summary(estimate_plot, varname = "fit_prob_amb", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = fit_prob_amb)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=fit_prob_amb-sd, ymax=fit_prob_amb+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Model-fitted outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))


```


```{r}
is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

estimate_plot$estimate_amb_mean <- rowMeans(data.frame(
  out1 = estimate$estimate_amb[estimate$out_level == 1],
  out2 = estimate$estimate_amb[estimate$out_level == 2],
  out3 = estimate$estimate_amb[estimate$out_level == 3],
  out4 = estimate$estimate_amb[estimate$out_level == 4]
))

tb2plot = data_summary(estimate_plot, varname = "estimate_amb_mean", groupnames = c("amb_level"))

ggplot(data = tb2plot, aes(x = amb_level, y = estimate_amb_mean)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=estimate_amb_mean-sd, ymax=estimate_amb_mean+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Estimated mean outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))
```

Compare estimated and model-fitted outcome probability
```{r}

is_med = 0
estimate_plot = estimate[estimate$is_med == is_med & estimate$out_level == 4, ]

estimate_plot$estimate_amb_mean <- rowMeans(data.frame(
  out1 = estimate$estimate_amb[estimate$out_level == 1],
  out2 = estimate$estimate_amb[estimate$out_level == 2],
  out3 = estimate$estimate_amb[estimate$out_level == 3],
  out4 = estimate$estimate_amb[estimate$out_level == 4]
))

compare <- rbind(
  data.frame(
    id = estimate_plot$id,
    amb_level = estimate_plot$amb_level,
    prob = estimate_plot$estimate_amb_mean,
    method = rep("estimate", nrow(estimate_plot))
  ), 
  data.frame(
    id = estimate_plot$id,
    amb_level = estimate_plot$amb_level,
    prob = estimate_plot$fit_prob_amb,
    method = rep("model-fit", nrow(estimate_plot))
  )
)

tb2plot = data_summary(compare, varname = "prob", groupnames = c("amb_level","method"))

ggplot(data = tb2plot, aes(x = amb_level, y = prob, fill = method)) +
  geom_bar(stat="identity", position=position_dodge(0.85), width = 0.8) +
  geom_errorbar(aes(ymin=prob-sd, ymax=prob+sd), width=0.1, size=1, position=position_dodge(0.85)) +
  # scale_fill_gradient2(low = "blue", high = "red") +
  # scale_fill_viridis(discrete = TRUE) + 
  # scale_fill_brewer(palette = "Greens") +
  scale_fill_brewer(palette = "Greens") +
  # scale_fill_viridis(discrete = TRUE, option="D") + 
  geom_hline(yintercept = 50, linetype= "dashed") +
  theme_classic() +
  ggtitle('Compare estimated and model-fitted outcome probability') +
  theme(axis.line = element_line(size = 1)) +
  theme(axis.ticks = element_line(size = 1, color = "black")) +
  theme(axis.text = element_text(size = 12, color = "black"))
```

# Compare model-predicted sv and subjective rating
## Load data
```{r}
path <- "E:/Ruonan/Projects in the lab/MDM Project/Medical Decision Making Imaging/MDM_imaging/Behavioral Analysis/Behavior Analysis"
setwd(path)
load("data_all_01272020.rda")

data_all$beta_t <- -data_all$beta

fit <- read.csv('MDM_model_fitting_parameters.csv', header = TRUE)
```

Take out the model-fitted parameters, monetary decisions
```{r}
fit_mon <- fit[fit$model== 'ambigNrisk' & fit$fitby == 'value', ] 
```

Calculate the model-fitting probability for ambiguity levels
```{r}
vals <- c(0, 5, 8, 12, 25)
fit_mon$sv_0 <- vals[1]^fit_mon$alpha
fit_mon$sv_1 <- vals[2]^fit_mon$alpha
fit_mon$sv_2 <- vals[3]^fit_mon$alpha
fit_mon$sv_3 <- vals[4]^fit_mon$alpha
fit_mon$sv_4 <- vals[5]^fit_mon$alpha

# fit_prob <- data.frame(id = fit_mon$id,
#                        is_med = fit_mon$is_med,
#                        )

fit_mon

colnames(fit_mon)[2:13]=c("alpha_mon", "alphase_mon", "beta_mon","betase_mon","gamma_mon","gammase_mon","LL_mon","r2_mon","AIC_mon","BIC_mon","model_mon","fitby_mon")


```

combine table
```{r}
data <- data_all[data_all$is_exclude_behavior == 0 & data_all$is_med == 0, ]

data <- merge(data, fit_mon, by=intersect(colnames(data), colnames(fit_mon)))
data
```

reorganize sheet
```{r}

idx = 1
monetary_level <- c(0, 5, 8, 12, 25)
for (val_level in c("0", "1", "2", "3", "4")) {
  

  estimate_single = data %>% select(id, contains(paste("rating", val_level, sep = "")), contains(paste("sv_", val_level, sep = "")))
  
  estimate_single$val_level = as.numeric(val_level)
  estimate_single$mon_level = as.numeric(monetary_level[c("0", "1", "2", "3", "4")==val_level])
  
  names(estimate_single)[2] = "rating" 
  names(estimate_single)[3] = "sv"
  
  
  # estimate_mon = data[data$is_med == 0,] %>% select((id), eval(parse(paste("estimate_", amb_level, "_", out_level, sep = ""))))
  # estimate_mon$out_level = as.numeric(out_level)
  # estimate_mon$amb_level = as.numeric(amb_level)
  
  if (idx == 1) {
    estimate = estimate_single
  } else {
    estimate = rbind(estimate, estimate_single)
  }
  
  idx = idx + 1

  
}

estimate$val_level = as.factor(estimate$val_level)
```

Calculate average
```{r}
ids <- unique(estimate$id)
length(ids)

```

## Normzlize model-estimated sv and subjective rating
```{r}
estimate_single$rating_norm = NA
estimate_single$sv_norm = NA

for (id in ids){
  estimate$rating_norm[estimate$id==id] <- scale(estimate$rating[estimate$id==id], center = TRUE, scale = TRUE)
  
    estimate$sv_norm[estimate$id==id] <- scale(estimate$sv[estimate$id==id], center = TRUE, scale = TRUE)
}

```

##Plot fitted value against rating
```{r}
alpha_value <- 0.5
ggplot(estimate, aes(x = sv_norm, y = rating_norm, color = id)) +
  geom_point(size = 2) + geom_line(size = 1, alpha = alpha_value) +
  scale_color_viridis(discrete = TRUE, option = "A") +
  theme(panel.background = element_rect(fill = "grey80")) +
  ggtitle('Comparing model-estimate subjective value and rating, Monetary')


```


##Plot fitted value against outcome level ($)
```{r}
alpha_value <- 0.5
ggplot(estimate, aes(x = mon_level, y = sv_norm, color = id)) +
  geom_point(size = 2) + geom_line(size = 1, alpha = alpha_value) +
  scale_color_viridis(discrete = TRUE, option = "A") +
  theme(panel.background = element_rect(fill = "grey80")) +
  ggtitle('Model-estimate subjective value, Monetary')

```

##Plot rating against outcome level ($)
```{r}
alpha_value <- 0.5
ggplot(estimate, aes(x = mon_level, y = rating_norm, color = id)) +
  geom_point(size = 2) + geom_line(size = 1, alpha = alpha_value) +
  scale_color_viridis(discrete = TRUE, option = "A") +
  theme(panel.background = element_rect(fill = "grey80")) +
  ggtitle('Rating, Monetary')

```


## recover alpha from rating, and compare with the model-fitted alpha

```{r}
# colnames(data)
vals_obj = c(0, 5, 8, 12, 25)
data$k <- NA
data$alpha_rec <- NA
```

plot
```{r}
for (sub_idx in 1:length(ids)) {
  vals <- as.numeric(estimate$rating_norm[estimate$id == ids[sub_idx]])
  vals <- vals - vals[1]
  fit_model <- nlsLM(vals ~ k*vals_obj^alpha, start = list(k = 1, alpha = 1), data = data.frame(vals, vals_obj))
  k <- coef(fit_model)[1]
  alpha_rec <- coef(fit_model)[2]
  data$k[data$id == ids[sub_idx]] <- k
  data$alpha_rec[data$id == ids[sub_idx]] <- alpha_rec
  plot(vals_obj, vals, main = c(paste(as.character(ids[sub_idx]),'recover'), paste('k=', round(k,3), '; alpha=', round(alpha_rec,3))))
  lines(seq(0,25,0.1), k*seq(0,25,0.1)^alpha_rec)
}

```

##plot model-fitting alpha against recovered alpha from ratings
```{r}
plot(data$alpha_mon, data$alpha_rec,
     xlab = "alpha, original model",
     ylab = "recovered alpha, rating")

abline(a=0, b=1)
```

Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
